---
title: "Clean data"
author: "Steven L. Peck and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

# Load and clean data

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(janitor)
library(here)

set.seed(1234)
```


```{r clean-data, warning=FALSE, message=FALSE, cache=TRUE}
# Constraints -------------------------------------------------------------

constraint_levels <- function(x) {
  filter(constraints, constraint == x) %>% 
    pull(levels_clean) %>%
    .[[1]]
}

constraints <- tribble(
  ~constraint, ~constraint_clean, ~levels_clean,
  "create_network", "Network creation", list("Network creation" = "T", "No network creation" = "F"),
  "select", "Selection", list("Selection" = "T", "No selection" = "F"),
  "disperse", "Dispersal", list("Dispersal" = "T", "No dispersal" = "F"),
  "compete", "Competition", list("Competition" = "T", "No competition" = "F"),
  "selectfor_d", "Selection for D", list("Selection" = "T", "No selection" = "F"),
  "catastrophe", "Catastrophe", list("Catastrophe" = "T", "No catastrophe" = "F")
)

saveRDS(constraints, here("data", "derived_data", "constraints.rds"))


# High/low ----------------------------------------------------------------

BHL <- read_rds(here("data", "raw_data", "BHL.rds")) %>% 
  clean_names(case = "snake") %>%   # Get rid of invalid characters in column names
  rename_all(list(~str_remove_all(., "yn$"))) %>%  # Get rid of "yn" in column names
  # Clean up constraint values
  mutate(create_network = fct_recode(create_network, !!!constraint_levels("create_network")),
         select = fct_recode(select, !!!constraint_levels("select")),
         disperse = fct_recode(disperse, !!!constraint_levels("disperse")),
         compete = fct_recode(compete, !!!constraint_levels("compete")),
         selectfor_d = fct_recode(selectfor_d, !!!constraint_levels("selectfor_d")),
         catastrophe = fct_recode(catastrophe, !!!constraint_levels("catastrophe"))) %>% 
  mutate_at(vars(one_of(constraints$constraint)), list(~ fct_inorder(.))) %>% 
  mutate(repp = factor(repp, levels = c(1, 2), labels = c("High", "Low"), ordered = TRUE))

BHL_small <- BHL %>% 
  group_by(repp) %>% 
  sample_frac(size = 0.1) %>% 
  ungroup()

sim_hl <- BHL_small %>% 
  # Make new columns with "_constraint" suffix that show if constraint is T/F
  # instead of using the label. e.g. "Selection" becomes TRUE, "No selection"
  # becomes FALSE
  mutate_at(vars(one_of(constraints$constraint)),
            list(constraint = ~as.logical(-as.integer(.) + 2L))) %>%
  # Count how many of the constraints are TRUE in each row
  mutate(n_constraints = reduce(select(., ends_with("_constraint")), `+`)) %>%
  # Make a factor version of the constraint count for plotting
  mutate(n_constraints_f = as.factor(n_constraints)) %>% 
  mutate(turnover_diff = landscape_linked_species_mean_turnover - landscape_unlinked_species_mean_turnover)

saveRDS(BHL, here("data", "derived_data", "BHL.rds"))
saveRDS(BHL_small, here("data", "derived_data", "BHL_small.rds"))
saveRDS(sim_hl, here("data", "derived_data", "sim_hl.rds"))


# Latin squares -----------------------------------------------------------

BLS <- read_rds(here("data", "raw_data", "BLS.rds")) %>% 
  clean_names(case = "snake") %>%   # Get rid of invalid characters in column names
  rename_all(list(~str_remove_all(., "yn$"))) %>%  # Get rid of "yn" in column names
  # Clean up constraint values
  mutate(create_network = fct_recode(create_network, !!!constraint_levels("create_network")),
         select = fct_recode(select, !!!constraint_levels("select")),
         disperse = fct_recode(disperse, !!!constraint_levels("disperse")),
         compete = fct_recode(compete, !!!constraint_levels("compete")),
         selectfor_d = fct_recode(selectfor_d, !!!constraint_levels("selectfor_d")),
         catastrophe = fct_recode(catastrophe, !!!constraint_levels("catastrophe"))) %>% 
  mutate_at(vars(one_of(constraints$constraint)), list(~fct_inorder(.)))

BLS_small <- BLS %>% 
  sample_frac(size = 0.1)

sim_ls <- BLS_small %>%
  # Make new columns with "_constraint" suffix that show if constraint is T/F
  # instead of using the label. e.g. "Selection" becomes TRUE, "No selection"
  # becomes FALSE
  mutate_at(vars(one_of(constraints$constraint)),
            list(constraint = ~as.logical(-as.integer(.) + 2L))) %>%
  # Count how many of the constraints are TRUE in each row
  mutate(n_constraints = reduce(select(., ends_with("_constraint")), `+`)) %>%
  # Make a factor version of the constraint count for plotting
  mutate(n_constraints_f = as.factor(n_constraints)) %>% 
  mutate(turnover_diff = landscape_linked_species_mean_turnover - landscape_unlinked_species_mean_turnover)

saveRDS(BLS, here("data", "derived_data", "BLS.rds"))
saveRDS(BLS_small, here("data", "derived_data", "BLS_small.rds"))
saveRDS(sim_ls, here("data", "derived_data", "sim_ls.rds"))
```


Create columns for every combination of constraint in the data (e.g. `select`, `select` & `disperse`, `select` & `disperse` & `create_network`, etc.)

(By the inimitable Vincent Arel-Bundock)

```{r cache=TRUE, warning=FALSE}
make_combinations <- function(df, m = 5) {
  com <- colnames(df)[2:ncol(df)] %>%
    combn(m) %>%
    as_tibble()
  out <- com %>%
    map(~ df[.]) %>%
    map(~ rowSums(.) == ncol(.)) %>%
    setNames(map(com, paste, collapse = " + ")) %>%
    as_tibble()
  return(out)
}

outcomes <- c("landscape_fitness_linked", "avg_evenness_t", "var_fitness", 
              "landscape_richness_mean", "landscape_linked_species_mean_turnover",
              "turnover_diff")

# High/low ----------------------------------------------------------------

# Select just the run number and *_constraint TRUE/FALSE columns
constraint_combinations_hl <- sim_hl %>%
  select(runnum, ends_with("_constraint")) %>%
  # Shrink names by removing "_constraint"
  rename_at(vars(ends_with("constraint")),
            list(~str_replace_all(., "_constraint", "")))

# Find all combinations of variables (m = number of items in combination; m = 2
# means pairs, m = 3 means triplets, etc.)
all_constraint_combos_hl <- map(2:6, ~make_combinations(constraint_combinations_hl, m = .)) %>%
  bind_cols(constraint_combinations_hl, .)

# Select the outcome variables we care about and join the constraint combinations
constraint_combo_outcomes_hl <- sim_hl %>%
  select(runnum, repp, n_constraints, one_of(outcomes)) %>%
  right_join(all_constraint_combos_hl, by = "runnum")

# Don't double count rows. If a row has two constraints like select and
# disperse, it'll also have select + disperse set to TRUE. If that's the case,
# we don't want to include it in just select or just disperse
constraint_combo_outcomes_hl_nested <- constraint_combo_outcomes_hl %>%
  select(-n_constraints) %>%
  # Make long
  gather(constraint_combo, value, -runnum, -repp, -one_of(outcomes)) %>%
  # Count how many constraints there are within each row based on + signs
  mutate(n = str_count(constraint_combo, "\\+") + 1) %>%
  # Only keep rows where the constraint is turned on
  filter(value == TRUE) %>%
  # Nest all the constraint combinations within each row
  group_by(runnum) %>%
  nest()

# Only keep the values where n == max(n) for that row
# This takes ≈2 minutes
constraint_combo_outcomes_hl_filtered <- constraint_combo_outcomes_hl_nested %>%
  mutate(filtered = data %>% map(~filter(., n == max(.$n)))) %>%
  select(-data) %>%
  unnest(filtered)

# This omitted all the rows where n_constraints == 0, so add those back in
no_constraints_hl <- constraint_combo_outcomes_hl %>%
  filter(n_constraints == 0) %>%
  mutate(constraint_combo = "No constraints", n = 0) %>%
  select(runnum, repp, one_of(outcomes), constraint_combo, n)

constraint_combo_outcomes_hl_done <- bind_rows(constraint_combo_outcomes_hl_filtered,
                                               no_constraints_hl) %>%
  select(-value)

saveRDS(constraint_combo_outcomes_hl_done, 
        here("data", "derived_data", "constraint_combo_outcomes_hl.rds"))


# Latin squares -----------------------------------------------------------

# Select just the run number and *_constraint TRUE/FALSE columns
constraint_combinations_ls <- sim_ls %>%
  select(runnum, ends_with("_constraint")) %>% 
  # Shrink names by removing "_constraint"
  rename_at(vars(ends_with("constraint")), 
            list(~str_replace_all(., "_constraint", "")))

# Find all combinations of variables (m = number of items in combination; m = 2
# means pairs, m = 3 means triplets, etc.)
all_constraint_combos_ls <- map(2:6, ~make_combinations(constraint_combinations_ls, m = .)) %>% 
  bind_cols(constraint_combinations_ls, .)

# Select the outcome variables we care about and join the constraint combinations
constraint_combo_outcomes_ls <- sim_ls %>%
  select(runnum, n_constraints, one_of(outcomes)) %>% 
  right_join(all_constraint_combos_ls, by = "runnum")

# Don't double count rows. If a row has two constraints like select and
# disperse, it'll also have select + disperse set to TRUE. If that's the case,
# we don't want to include it in just select or just disperse
constraint_combo_outcomes_ls_nested <- constraint_combo_outcomes_ls %>% 
  select(-n_constraints) %>% 
  # Make long
  gather(constraint_combo, value, -runnum, -one_of(outcomes)) %>% 
  # Count how many constraints there are within each row based on + signs
  mutate(n = str_count(constraint_combo, "\\+") + 1) %>%
  # Only keep rows where the constraint is turned on
  filter(value == TRUE) %>%
  # Nest all the constraint combinations within each row
  group_by(runnum) %>% 
  nest()

# Only keep the values where n == max(n) for that row
# This takes ≈1 minute
constraint_combo_outcomes_ls_filtered <- constraint_combo_outcomes_ls_nested %>% 
  mutate(filtered = data %>% map(~filter(., n == max(.$n)))) %>% 
  select(-data) %>% 
  unnest(filtered)

# This omitted all the rows where n_constraints == 0, so add those back in
no_constraints_ls <- constraint_combo_outcomes_ls %>% 
  filter(n_constraints == 0) %>% 
  mutate(constraint_combo = "No constraints", n = 0) %>% 
  select(runnum, one_of(outcomes), constraint_combo, n)

constraint_combo_outcomes_ls_done <- bind_rows(constraint_combo_outcomes_ls_filtered,
                                               no_constraints_ls) %>% 
  select(-value)

saveRDS(constraint_combo_outcomes_ls_done, 
        here("data", "derived_data", "constraint_combo_outcomes_ls.rds"))
```


Data details:

- High-low full: `r scales::comma(nrow(BHL))` rows
    - High: `r scales::comma(nrow(filter(BHL, repp == "High")))` rows
    - Low: `r scales::comma(nrow(filter(BHL, repp == "Low")))` rows
- High-low small: `r scales::comma(nrow(BHL_small))` rows
    - High: `r scales::comma(nrow(filter(BHL_small, repp == "High")))` rows
    - Low: `r scales::comma(nrow(filter(BHL_small, repp == "Low")))` rows
- Latin squares full: `r scales::comma(nrow(BLS))` rows
- Latin squares small: `r scales::comma(nrow(BLS_small))` rows


\

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div> 
